### 2016-05-03 ch05-initvals/initial-values.tex
Fix some references
Clean up CH05 figure directory

\begin{figure}[tbh]
\centering
\input{\thisDir/fig/oesetup.tikz}
\caption[Output-error set-up.]{SISO LTI discrete-time system in an output error setup.}
\label{fig:oesetup}
\end{figure}

@@

\subsection{Initial Estimates Procedure}\label{sec:init:procedures}
\begin{figure}[p]
  \centering
  \includegraphics[width=\columnwidth]{\thisDir/fig/flowgraph}
  \caption[Flow chart of different initialization procedures.]{Flow chart depicting the different estimation procedures, from left to right: \circledNum{1} an approach using the true model as initial estimate; \circledNum{2} an existing approach using \gls{BTLS} and \gls{GTLS} starting values, and the novel initialization strategies outlined in this chapter (\circledNum{3}, \circledNum{4}) that make use of smoothers to generate improved starting values for the non-convex optimization problem.
  The flow of non-parametric data is depicted by full arrows, with the \gls{FRF} data marked by asterisks. Parametric models are indicated by dashed, unfilled arrows.} 
  \label{fig:flowgraph}
\end{figure}

@@

\item \emph{Local polynomial method (LPM) with truncation}
\disclaimer{The time-truncated \gls{LPM} has been explained in \secref{sec:nparam:trunc} in more detail. The pertinent details are repeated here to aid readability.}
A good estimate of the \gls{FRF} of the chosen system can be obtained via the truncated \gls{LPM}, which is summarized as follows~\citep{Lumori2014TIM} and \secref{sec:nonparametric:truncation} of this thesis.
Here, we repeat the main points briefly.
The \gls{LPM} is first applied to estimate the \gls{FRF} from a full input/output data record of the \gls{SISO} system.
The smooth characteristics of both the exact \gls{FRF} $\true{G}$ and the transient term $T$ allow for application of the \gls{LPM}, leading to a smooth \gls{FRF} estimate with the transient and noise suppressed.

@@

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.8\columnwidth}
  \setlength{\figureheight}{0.6\figurewidth}
  \input{\thisDir/fig/exampleSystems.tikz}
 % \caption{Results of an example of Monte Carlo simulation.}
 \caption[Bodeplot of successful ad failed estimates.]{Illustrative Bode plots of a few successful~\legref{leg:example-good-estimate} and `failed'~\legref{leg:example-bad-estimate} estimates $\model{\bullet}$ for both systems $\true{G}$~\legref{leg:example-exact} under test.
 The `failed' estimates are caused by local minima in the cost function.
 Success or failure is determined using the criterion in equation~\eqref{eq:successrateTol}. The $3\unit{dB}$ bandwidth of each system is highlighted~\legref{leg:example-3db-bandwidth}.}
\label{fig:exampleFRF}
\end{figure}

@@

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.8\columnwidth}
  \setlength{\figureheight}{0.6\figurewidth}
  \input{\thisDir/fig/MC-RFIR-1.11111dBSNR36pts3dB-ripple6dB.tikz}
 \caption[Model error for different initialization schemes on simulations.]{The distance $\|\model{\bullet} - \hat{G}_0 \|_2$  between the different estimates ($\model{exist}$~\legref{leg:dist-G-exist}, $\model{trunc}$~\legref{leg:dist-G-trunc} and $\model{RFIR}$~\legref{leg:dist-G-RFIR} ) and the `best theoretical' estimates ($\model{0}$) shows that the smoothers help the estimate to converge to $\model{0}$.
 The same measure is shown for the initial values $\model[init]{RFIR}$ \legref{leg:dist-G-RFIR-init} and $\model[init]{trunc}$ \legref{leg:dist-G-trunc-init}.
 $\|{G}_{0} - \hat{G}_0\|_2$\legref{leg:dist-G0} shows how far the true model and `best theoretical' estimates are apart to put the other distances into perspective. }
  \label{fig:single-sim}
\end{figure}

@@

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/fig/successRates.tikz}
 \caption[Simulated success rate of the different initialization schemes for varying SNR.]{The success rate $\successRate$  obtained using the smoothers, i.e. $\model{RFIR}$~\legref{leg:success-RFIR} and $\model{trunc}$~\legref{leg:success-LPMTrunc}, are significantly higher than for the existing methods $\model{exist}$~\legref{leg:success-existing} in most of the studied range of \glspl{SNR}, number of samples and for both test systems. The $95\%$ confidence intervals~\eqref{eq:initvals:Binomial:CI} are indicated by bars.}
  \label{fig:successRateVS_SNR36N3dB}
\end{figure}

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.66\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/fig/RMSEvs_SNR36N3dB-ripple6.tikz}
 \caption[Simulated model RMSE compared to rule-of-thumb.]{The accordance between the observed \gls{RMSE} of $\hat{G}_0$~\legref{leg:RMSE:delta:observed}(with $\pm2\sigma$ interval) and the rule-of-thumb~\eqref{eq:heur-RMSE}\legref{leg:RMSE:rule-of-thumb} shows how well $\model{\trueSymbol}$ approximates the true system $\true{G}$.
 In the bottom plot, the difference between both is shown.
 Consequently, it makes sense to examine the behavior of the models in terms of $\model{\trueSymbol}$ as long as this RMSE meets the user's requirements.}
  \label{fig:RMSE}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.6\columnwidth]{\thisDir/fig/measurement.pdf}
  \caption[Measurement schematic of \BK\ 1613 filter.]{Schematic representation of the measurement set-up for the \BK\ 1613 filter. The AWG (Arbitrary Waveform Generator) and DAQ (Data Acquisition) hardware share the same clock and are thus synchronized. 
  Blue arrows indicate coax cables. 
  At the output of the bandpass filter, a noise generator is added that buffers the incoming signal using a TL071 opamp and adds white noise before passing the signal to the DAQ.} 
  \label{fig:measurementSetup}
\end{figure}

@@

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.75\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/fig/bode-bk1613.tikz}
  \caption[\BK{} 1613 filter transfer function]{Transfer function of the considered \BK{} 1613 filter.
  The empirical transfer function estimates $Y^{[r]}(\omega)/U^{[r]}(\omega)$~\legref{leg:bk1613:ETFE} and its average $\tilde{Y}(\omega)/\tilde{U}(\omega)$~\legref{leg:bk1613:meanETFE} obtained from the Elvis measurements are shown together with the estimated reference model $G_{\mathrm{VXI}}$~\legref{leg:bk1613:vxi}.} 
  \label{fig:bk1613}
\end{figure}

@@

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.75\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/fig/elvis-spectra.tikz}
  \caption[Measured input/output spectra of \BK{} filter.]{Average input $\tilde{U}(\omega)$ and output $\tilde{Y}(\omega)$ spectra \legref[2]{leg:SpectraMeasurement:U:mean} measured using the Elvis and the noise levels $\hat\sigma_U$ and $\hat\sigma_Y$  \legref[2]{leg:SpectraMeasurement:U:noise}.}
  \label{fig:SpectraMeasurement}
\end{figure}

@@

\begin{figure}[p]
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \setlength{\figurewidth}{0.75\columnwidth}
  \input{\thisDir/fig/CostFunctionsMLE-measurement.tikz}
  \caption[Cost function values over the different measurements.]{Cost function values $V(\theta)$ obtained during the different realizations of the measurement.
  The bottom plot shows a linear zoom of the top plot.
  For each method, the inter-quartile range~\legref{leg:costMeasurements:best:iqr}, median~\legref{leg:costMeasurements:best:median} and individual values~\legref{leg:costMeasurements:best:data} are shown.
  This implies that a lower (local) minimum of the cost function can be attained using these smoothing techniques.}
  \label{fig:costMeasurements}
\end{figure}

@@

\begin{figure}[p]
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \setlength{\figurewidth}{0.75\columnwidth}
  \input{\thisDir/fig/meas-validation.tikz}
  \caption[Validation cost of the different measurements.]{Validation of the measured models. 
  For each method, the distance \eqref{eq:measurementCriterion} between the estimates and $\model{VXI}$ is shown~\legref{leg:validationMeasurements:best:data} together with the median~\legref{leg:validationMeasurements:best:median} and inter-quartile range~\legref{leg:validationMeasurements:best:iqr}.
  $\norm{G_{\mathrm{VXI}}}$\legref{leg:validationMeasurements:H2Norm} is shown as a reference.
  The bottom plot shows a linear zoom of the top plot.
  The proposed methods yield models that are closer to $\model{VXI}$ than the existing $\model{exist}$.
  The results are in line with the values of the cost function in \figref{fig:costMeasurements}.}
  \label{fig:validationMeasurements}
\end{figure}
\begin{table}[p]
  \centering
  \caption{Observed percentiles of the validation distance $\norm[2]{\model{\bullet}-G_{\mathrm{VXI}}}$.}
  \input{\thisDir/tables/meas-validation-quantiles.tbl.tex}
\label{tbl:validationMeasurements}
\end{table}

@@

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/fig/overview-cost-val.tikz}
  \caption[$\costFunc{\bullet}$ and $\validationDistance{\bullet}$ for each repeated measurement.]{Cost function $V(\model{\bullet})$ and validation distance of the model estimated in each repetition of the measurement.
  Based on the cost function, $\model{RFIR}$~\legref{leg:RFIR} is not always the best estimate $\model{best}$~\legref{leg:best}.
  Especially in the validation plot (bottom), $\model{RFIR}$ performs (almost) as well or even better than $\model{exist}$~\legref{leg:exist} and $\model{trunc}$~\legref{leg:trunc}.
  Both latter methods often produce models that perform poorly compared to $\norm[2]{G_{\mathrm{VXI}} }$~\legref{leg:reference} and $\model{VXI}$~\legref{leg:VXI}.
  This means that in our limited experimental study, the performance degradation of choosing RFIR to produce initial values over the studied alternatives is small.}
  \label{fig:overview}
\end{figure}

\begin{figure}
  \centering
  % \ref{leg:init:secondBest}
  \setlength{\figurewidth}{0.75\columnwidth}
  \setlength{\figureheight}{0.60\figurewidth}
  \input{\thisDir/fig/special-histogram.tikz}
  \caption[Performance degradation/enhancement for selecting the second best model.]{
  Performance degradation/enhancement ($X_{\bullet}-X_{\mathrm{best}}$) for choosing a given method $\bullet$ instead of the `best' method for the measurement example in this chapter.
  The markers show individual observations and the boxes show the \gls{IQR}.
  The dashed lines are the minimum, median and maximum of $X_{\bullet}$ to give a sense of scale.
  On average there is little to gain or lose from using $\model{RFIR}$ instead of $\model{best}$.
  For $\model{exist}$ and $\model{trunc}$, the situation is a lot less favorable.
  }
  \label{fig:init:histogramEnhancement}
\end{figure}

@@

\begin{figure}[p]
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \centering
  \input{\thisDir/fig/bodeplots.tikz}
  \caption[Bode plots of the stress test filters.]{Bode plots of the tested filters~\legref{leg:bode:true} in the stress test. 
  For each filter, two (randomly selected) instances of the parametric estimates $\model{\bullet}$ are shown per method.
  }
  \label{fig:bodeplots}
\end{figure}

\begin{figure}[p]
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \centering
  \input{\thisDir/fig/distances.tikz}
  \caption[Empirical \glsentrytext{CDF} of $\validationDistance{\bullet}$ in the stress test.]{Empirical cumulative distribution function of the validation distance $D_{\bullet} = \norm{\model{\bullet} - \true{G}}$ for the different tested systems (different numbered plots) and the different initial values (colors).
  Note that since $\norm{\true{G}}=1$ is chosen, $D_{\bullet}$ immediately indicates the relative RMS error of the estimates.
  }
  \label{fig:distancesStress}
\end{figure}

>>>>

\begin{figure}[tbh]
\centering
\input{\thisDir/figs/oesetup.tikz}
\caption[Output-error set-up.]{SISO LTI discrete-time system in an output error setup.}
\label{fig:oesetup}
\end{figure}

@@

\subsection{Initial Estimates Procedure}\label{sec:init:procedures}
\begin{figure}[p]
  \centering
  \includegraphics[width=\columnwidth]{\thisDir/figs/flowgraph}
  \caption[Flow chart of different initialization procedures.]{Flow chart depicting the different estimation procedures, from left to right: \circledNum{1} an approach using the true model as initial estimate; \circledNum{2} an existing approach using \gls{BTLS} and \gls{GTLS} starting values, and the novel initialization strategies outlined in this chapter (\circledNum{3}, \circledNum{4}) that make use of smoothers to generate improved starting values for the non-convex optimization problem.
  The flow of non-parametric data is depicted by full arrows, with the \gls{FRF} data marked by asterisks. Parametric models are indicated by dashed, unfilled arrows.} 
  \label{fig:flowgraph}
\end{figure}

@@

\item \emph{Local polynomial method (LPM) with truncation}
\disclaimer{The time-truncated \gls{LPM} has been explained in \secref{sec:nonparametric:truncation} in more detail. The pertinent details are repeated here to aid readability.}
A good estimate of the \gls{FRF} of the chosen system can be obtained via the truncated \gls{LPM}, which is summarized as follows~\citep{Lumori2014TIM} and \secref{sec:nonparametric:truncation} of this thesis.
Here, we repeat the main points briefly.
The \gls{LPM} is first applied to estimate the \gls{FRF} from a full input/output data record of the \gls{SISO} system.
The smooth characteristics of both the exact \gls{FRF} $\true{G}$ and the transient term $T$ allow for application of the \gls{LPM}, leading to a smooth \gls{FRF} estimate with the transient and noise suppressed.

@@

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.8\columnwidth}
  \setlength{\figureheight}{0.6\figurewidth}
  \input{\thisDir/figs/exampleSystems.tikz}
 % \caption{Results of an example of Monte Carlo simulation.}
 \caption[Bodeplot of successful ad failed estimates.]{Illustrative Bode plots of a few successful~\legref{leg:example-good-estimate} and `failed'~\legref{leg:example-bad-estimate} estimates $\model{\bullet}$ for both systems $\true{G}$~\legref{leg:example-exact} under test.
 The `failed' estimates are caused by local minima in the cost function.
 Success or failure is determined using the criterion in equation~\eqref{eq:successrateTol}. The $3\unit{dB}$ bandwidth of each system is highlighted~\legref{leg:example-3db-bandwidth}.}
\label{fig:exampleFRF}
\end{figure}

@@

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.8\columnwidth}
  \setlength{\figureheight}{0.6\figurewidth}
  \input{\thisDir/figs/MC-SNR1.1dB-NBW36-Q6dB.tikz}
 \caption[Model error for different initialization schemes on simulations.]{The distance $\|\model{\bullet} - \hat{G}_0 \|_2$  between the different estimates ($\model{exist}$~\legref{leg:dist-G-exist}, $\model{trunc}$~\legref{leg:dist-G-trunc} and $\model{RFIR}$~\legref{leg:dist-G-RFIR} ) and the `best theoretical' estimates ($\model{0}$) shows that the smoothers help the estimate to converge to $\model{0}$.
 The same measure is shown for the initial values $\model[init]{RFIR}$ \legref{leg:dist-G-RFIR-init} and $\model[init]{trunc}$ \legref{leg:dist-G-trunc-init}.
 $\|{G}_{0} - \hat{G}_0\|_2$\legref{leg:dist-G0} shows how far the true model and `best theoretical' estimates are apart to put the other distances into perspective. }
  \label{fig:single-sim}
\end{figure}

@@

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/figs/successRates.tikz}
 \caption[Simulated success rate of the different initialization schemes for varying SNR.]{The success rate $\successRate$  obtained using the smoothers, i.e. $\model{RFIR}$~\legref{leg:success-RFIR} and $\model{trunc}$~\legref{leg:success-LPMTrunc}, are significantly higher than for the existing methods $\model{exist}$~\legref{leg:success-existing} in most of the studied range of \glspl{SNR}, number of samples and for both test systems. The $95\%$ confidence intervals~\eqref{eq:initvals:Binomial:CI} are indicated by bars.}
  \label{fig:successRateVS_SNR36N3dB}
\end{figure}

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.66\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/figs/RMSEvs_SNR36N3dB-ripple6.tikz}
 \caption[Simulated model RMSE compared to rule-of-thumb.]{The accordance between the observed \gls{RMSE} of $\hat{G}_0$~\legref{leg:RMSE:delta:observed}(with $\pm2\sigma$ interval) and the rule-of-thumb~\eqref{eq:heur-RMSE}\legref{leg:RMSE:rule-of-thumb} shows how well $\model{\trueSymbol}$ approximates the true system $\true{G}$.
 In the bottom plot, the difference between both is shown.
 Consequently, it makes sense to examine the behavior of the models in terms of $\model{\trueSymbol}$ as long as this RMSE meets the user's requirements.}
  \label{fig:RMSE}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.6\columnwidth]{\thisDir/figs/measurement.pdf}
  \caption[Measurement schematic of \BK\ 1613 filter.]{Schematic representation of the measurement set-up for the \BK\ 1613 filter. The AWG (Arbitrary Waveform Generator) and DAQ (Data Acquisition) hardware share the same clock and are thus synchronized. 
  Blue arrows indicate coax cables. 
  At the output of the bandpass filter, a noise generator is added that buffers the incoming signal using a TL071 opamp and adds white noise before passing the signal to the DAQ.} 
  \label{fig:measurementSetup}
\end{figure}

@@

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.75\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/figs/bode-bk1613.tikz}
  \caption[\BK{} 1613 filter transfer function]{Transfer function of the considered \BK{} 1613 filter.
  The empirical transfer function estimates $Y^{[r]}(\omega)/U^{[r]}(\omega)$~\legref{leg:bk1613:ETFE} and its average $\tilde{Y}(\omega)/\tilde{U}(\omega)$~\legref{leg:bk1613:meanETFE} obtained from the Elvis measurements are shown together with the estimated reference model $G_{\mathrm{VXI}}$~\legref{leg:bk1613:vxi}.} 
  \label{fig:bk1613}
\end{figure}

@@

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.75\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/figs/elvis-spectra.tikz}
  \caption[Measured input/output spectra of \BK{} filter.]{Average input $\tilde{U}(\omega)$ and output $\tilde{Y}(\omega)$ spectra \legref[2]{leg:SpectraMeasurement:U:mean} measured using the Elvis and the noise levels $\hat\sigma_U$ and $\hat\sigma_Y$  \legref[2]{leg:SpectraMeasurement:U:noise}.}
  \label{fig:SpectraMeasurement}
\end{figure}

@@

\begin{figure}[p]
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \setlength{\figurewidth}{0.75\columnwidth}
  \input{\thisDir/figs/CostFunctionsMLE-measurement.tikz}
  \caption[Cost function values over the different measurements.]{Cost function values $V(\theta)$ obtained during the different realizations of the measurement.
  The bottom plot shows a linear zoom of the top plot.
  For each method, the inter-quartile range~\legref{leg:costMeasurements:best:iqr}, median~\legref{leg:costMeasurements:best:median} and individual values~\legref{leg:costMeasurements:best:data} are shown.
  This implies that a lower (local) minimum of the cost function can be attained using these smoothing techniques.}
  \label{fig:costMeasurements}
\end{figure}

@@

\begin{figure}[p]
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \setlength{\figurewidth}{0.75\columnwidth}
  \input{\thisDir/figs/meas-validation.tikz}
  \caption[Validation cost of the different measurements.]{Validation of the measured models. 
  For each method, the distance \eqref{eq:measurementCriterion} between the estimates and $\model{VXI}$ is shown~\legref{leg:validationMeasurements:best:data} together with the median~\legref{leg:validationMeasurements:best:median} and inter-quartile range~\legref{leg:validationMeasurements:best:iqr}.
  $\norm{G_{\mathrm{VXI}}}$\legref{leg:validationMeasurements:H2Norm} is shown as a reference.
  The bottom plot shows a linear zoom of the top plot.
  The proposed methods yield models that are closer to $\model{VXI}$ than the existing $\model{exist}$.
  The results are in line with the values of the cost function in \figref{fig:costMeasurements}.}
  \label{fig:validationMeasurements}
\end{figure}
\begin{table}[p]
  \centering
  \caption{Observed percentiles of the validation distance $\norm[2]{\model{\bullet}-G_{\mathrm{VXI}}}$.}
  \input{\thisDir/tables/meas-validation-quantiles.tbl.tex}
\label{tbl:validationMeasurements}
\end{table}

@@

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \input{\thisDir/figs/overview-cost-val.tikz}
  \caption[$\costFunc{\bullet}$ and $\validationDistance{\bullet}$ for each repeated measurement.]{Cost function $V(\model{\bullet})$ and validation distance of the model estimated in each repetition of the measurement.
  Based on the cost function, $\model{RFIR}$~\legref{leg:RFIR} is not always the best estimate $\model{best}$~\legref{leg:best}.
  Especially in the validation plot (bottom), $\model{RFIR}$ performs (almost) as well or even better than $\model{exist}$~\legref{leg:exist} and $\model{trunc}$~\legref{leg:trunc}.
  Both latter methods often produce models that perform poorly compared to $\norm[2]{G_{\mathrm{VXI}} }$~\legref{leg:reference} and $\model{VXI}$~\legref{leg:VXI}.
  This means that in our limited experimental study, the performance degradation of choosing RFIR to produce initial values over the studied alternatives is small.}
  \label{fig:overview}
\end{figure}

\begin{figure}
  \centering
  % \ref{leg:init:secondBest}
  \setlength{\figurewidth}{0.75\columnwidth}
  \setlength{\figureheight}{0.60\figurewidth}
  \input{\thisDir/figs/special-histogram.tikz}
  \caption[Performance degradation/enhancement for selecting the second best model.]{
  Performance degradation/enhancement ($X_{\bullet}-X_{\mathrm{best}}$) for choosing a given method $\bullet$ instead of the `best' method for the measurement example in this chapter.
  The markers show individual observations and the boxes show the \gls{IQR}.
  The dashed lines are the minimum, median and maximum of $X_{\bullet}$ to give a sense of scale.
  On average there is little to gain or lose from using $\model{RFIR}$ instead of $\model{best}$.
  For $\model{exist}$ and $\model{trunc}$, the situation is a lot less favorable.
  }
  \label{fig:init:histogramEnhancement}
\end{figure}

@@

\begin{figure}[p]
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \centering
  \input{\thisDir/figs/bodeplots.tikz}
  \caption[Bode plots of the stress test filters.]{Bode plots of the tested filters~\legref{leg:bode:true} in the stress test. 
  For each filter, two (randomly selected) instances of the parametric estimates $\model{\bullet}$ are shown per method.
  }
  \label{fig:bodeplots}
\end{figure}

\begin{figure}[p]
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.68\figurewidth}
  \centering
  \input{\thisDir/figs/distances.tikz}
  \caption[Empirical \glsentrytext{CDF} of $\validationDistance{\bullet}$ in the stress test.]{Empirical cumulative distribution function of the validation distance $D_{\bullet} = \norm{\model{\bullet} - \true{G}}$ for the different tested systems (different numbered plots) and the different initial values (colors).
  Note that since $\norm{\true{G}}=1$ is chosen, $D_{\bullet}$ immediately indicates the relative RMS error of the estimates.
  }
  \label{fig:distancesStress}
\end{figure}
